

\begin{thebibliography}{9}
    \bibitem{haupt} 
    R. L. Haupt and S. E. Haupt
    \textit{Practical genetic algorithms.} 
    John Wiley \& Sons, 2004.

    \bibitem{Mitchell} 
    T. Mitchell.
    \textit{Machine Learning}. 
    McGraw Hill, 1997
    
    \bibitem{Brandimarte} 
    P. Brandimarte, “Routing and scheduling in a flexible job shop by tabu search,”
    \textit{Annals of Operations Research}, 
    vol. 41, p. 157183, 1993.

    \bibitem{GareyJohnson} 
    M. R. Garey, D. S. Johnson, R. Sethi, The complexity of flowshop and jobshop scheduling, Math. Oper. Res., vol. 1, no. 2, 1976, pp. 117–129.
    
    \bibitem{GareyJohnsonTheoryNP} 
    M. R. Garey, D. S. Johnson.
    \textit{Computers and Intractability: A Guide to the Theory of NP-Completeness}. 
    , 1979
    
    \bibitem{BlumRoli} 
    C. Blum, A. Roli, Metaheuristics in combinatorial optimization: Overview
    and conceptual comparison, ACM Computing Surveys 35 (3) (2003) 268–
    308
    
    \bibitem{YuanYuan} 
    Y. Yuan, H. Xu
    \textit{Flexible job shop scheduling using hybrid differential evolution algorithms}. 
    Computers \& Industrial Engineering, Volume 65, Issue 2, June 2013, Pages 246-260

    \bibitem{Apolloni} 
    J. M. Apolloni
    \textit{Propuesta de Metaheurísticas Híbridas para Mejorar el Análisis de Datos en Bioinformática (Ph.D. Tesis)}.
    Universidad Nacional de San Luis, 2017.
    
    \bibitem{Talbi} 
    E.-G. Talbi. A taxonomy of hybrid metaheuristics.
    \textit{Journal of Heuristics,}.
    8:541–564, 2002.
    
    \bibitem{openMP} 
    B. Chapman and G. Jost and R. van der Pas, 
    \textit{Using OpenMP: Portable Shared Memory Parallel Programming.}.
    MIT Press, 2007
    
    \bibitem{Ali} 
    M. Ali, W.A Zhu, Penalty function-based differential evolution algorithm for constrained global optimization, Comput. Optim. Appl., 54, 2013, pp. 707-739.
     
    \bibitem{Juang} 
    J.-G. Juang, S.-T. Yu, Disturbance encountered landing system design based on sliding mode control with evolutionary computation and cerebellar model articulation controller, Appl. Math. Model., 39, 2015, pp. 5862-5881.
     
    \bibitem{Yang} 
    Z. Yang, Q. Yu, W. Dong, X. Gu, W. Qiao, X. Liang, Structure control classification and optimization model of hollow carbon nanosphere core polymer particle based on improved differential evolution support vector machine, Appl. Math. Model., 37, 2013, pp. 7442-7451

    \bibitem{Garey} 
    M. R. Garey, D. S. Johnson, \& R. Sethi, The complexity of flowshop and jobshop scheduling.
    \textit{Mathematics of Operations Research,}.
     1, 117–129, 1976.
    
    \bibitem{albaMeta2005} 
     E. Alba,
    \textit{Parallel Metaheuristics: A New Class of Algorithms.}
     Wiley, 2005.
    
    \bibitem{bierwirth1995} 
    C. Bierwirth (1995). 
    A generalized permutation approach to job-shop scheduling with genetic algorithms. 
    Operations Research Spektrum. Vol. 17 (2). pp 87/92. 

    
    \bibitem{LuqueAlba} 
    G. Luque and E. Alba,
    \textit{Parallel Genetic Algorithms: Theory and Real World Ap-plications.}
    Springer Publishing Company, Incorporated, 2013.

    \bibitem{Goldberg} 
    D. E. Goldberg.
    \textit{Genetic Algorithms in Search, Optimization and Machine Learning}. 
    Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1st edition, 1989.

    \bibitem{GarciaNietoAlba} 
    J. García-Nieto and E. Alba. Hybrid PSO6 for hard continuous optimization.
    \textit{Soft Computing}. 
    pages 1–19, 2014

    \bibitem{DorigoCaro} 
    M. Dorigo and G. Di Caro.
    \textit{New ideas in optimization}. 
    1999.
    
    \bibitem{Brownlee} 
    J. Brownlee.
    \textit{Clever Algorithms: Nature-inspired programming recipes.} 
    Jason Brownlee, 2011.
    
    \bibitem{Garcia-Nieto} 
    J. García-Nieto
    \textit{Emergent Optimization: Design and Applications in Telecomunications and Bioinformatics (Ph.D. Thesis).}
    University of Málaga, 2013.
    
    \bibitem{LaarhovenAarts} 
    P. J. M. Van Laarhoven and E. H. L. Aarts
    \textit{Simulated annealing.}
    Springer, 1987.

    \bibitem{LourencoStutzle} 
    H. R. Lourenço, O. C. Martin, and T. Stützle.
    \textit{Iterated local search.}
    Springer, 2003.
    
    \bibitem{HansenMladenovicBrimbergPerez} 
    P. Hansen, N. Mladenovic, J. Brimberg, and J. A. M. Pérez.
    \textit{Variable neighborhood search.} 
    In Handbook of Metaheuristics, pages 61–86. Springer, 2010.

    \bibitem{GendreauPotvin} 
    M. Gendreau and J-Y. Potvin
    \textit{Handbook of metaheuristics.}
    volume 2. Springer, 2010.

    \bibitem{PriceStornLampinen} 
    K. V. Price, R. Storn, and J. Lampinen
    \textit{Differential Evolution: A practical Approach to Global Optimization.}
    Springer-Verlag, London, UK, 2005.

    \bibitem{StornPrice} 
    R. Storn and K. V. Price. 
    Differential evolution: A simple and efficient adaptive scheme for global optimization over continuous spaces. 
     Technical report, TR95012-ICSI, 1995.

    \bibitem{StornPrice2} 
    R. Storn, K. Price Differential evolution—a simple and efficient heuristic for global optimization over continuous spaces. 
    \textit{Journal of Global Optimization.}
    1997;11(4):341–359. 
    
    \bibitem{Colorni} 
    A. Colorni, M. Dorigo, V. Maniezzo Distributed optimization by ant colonies. Proceedings of the 1st European Conference on Artificial Life; 1991; Paris, France. pp. 134–142.
    
    \bibitem{StornPriceConference} 
    R. Storn and K. V. Price. 
    Minimizing the real functions of the ICEC’96 contest by differential evolution. 
    In \textit{International Conference on Evolutionary Computation},pages 842–844, 1996.

    \bibitem{KennedyEberhartShi} 
    J. Kennedy, R. Eberhart, and Y. Shi.
    \textit{Swarm Intelligence}. 
    Morgan Kaufmann, San Francisco, CA, 2001.
    
    \bibitem{Eberhart} 
    R. C. Eberhart, J. Kennedy New optimizer using particle swarm theory. Proceedings of the 6th International Symposium on Micro Machine and Human Science; October 1995. pp. 39–43.
    
    \bibitem{BlumLi} 
    C. Blum and X. Li.
    \textit{Swarm intelligence in optimization}. 
    Springer, 2008.

    \bibitem{Dasgupta} 
    D. Dasgupta.
    \textit{Artificial immune systems and their applications}. 
    Springer Publishing Company, Incorporated, 2014.  
    
    
    \bibitem{KirkpatrickVecchi} 
    S. Kirkpatrick, M. P. Vecchi, et al. 
    \textit{Optimization by simmulated annealing.}
    Science, 220(4598):671–680, 1983.  

    \bibitem{Cerny} 
    V. Cerny. Thermodynamical approach to the traveling salesman problem: An 
    efficient simulation algorithm. 
    \textit{Journal of optimization theory and applications}
    , 45(1):41–51, 1985.  
    
    \bibitem{MetropolisRosenbluth} 
    N. Metropolis, A. Rosenbluth, M. Rosenbluth, A. Teller, and E. Teller. Equation of state
    calculations by fast computing machines.
    \textit{Journal of Chemical Physics,}. 
    21:1087–1092, 1953.  
    
    \bibitem{HansenMladenovic} 
    P. Hansen and N. Mladenovic. Variable neighborhood search: Principles and applications.
    \textit{European Journal of Operational Research, }. 
    130(3):449–467, 2001.  
    
    \bibitem{QinSuganthan} 
    A.K. Qin and P.N. Suganthan. Self-adaptive differential evolution algorithm for numerical optimization. In
    \textit{Proceedings of the 2005 IEEE Congress on Evolutionary Computation }. 
    , volume 2, pages 1785–1791, 2005.      
    
    \bibitem{BrestGreinerBoskovicMernik} 
    J. Brest, S. Greiner, B. Boskovic, M. Mernik, and V. Zumer. Self-adapting control
    parameters in differential evolution: A comparative study on numerical benchmark
    problems.
    \textit{s. IEEE Transactions on Evolutionary Computation, }. 
    10(6):646–657, 2006.   
    
    \bibitem{Holland} 
     J. H. Holland. Outline for a logical theory of adaptive systems.
    \textit{Journal of the ACM}. 
    3:297–314, 1962.
    
    \bibitem{Holland2} 
     J. H. Holland.
    \textit{Adaptation in Natural and Artificial Systems}. 
    University of Michigan Press, Ann Arbor, MI, 1975.

    \bibitem{Holland3} 
    J. H. Holland 
    \textit{Adaptation in Natural and Artificial Systems: An Introductory Analysis with Applications to Biology, Control, and Artificial Intelligence}. 
    MIT Press; 1992.


    \bibitem{Rechenberg} 
    I. Rechenberg.
    Cybernetic solution path of an experimental problem. 
    Technical Report, Royal Aircraft Establishment Library Translation No. 1112, Farnborough, UK, 1965.

    \bibitem{Rechenberg2} 
    I. Rechenberg.
    \textit{Evolutionstrategie: Optimierung technischer systeme nach prinzipien der biologischen evolution.}. 
    Frommann-Holzboog, 1973.

    \bibitem{Schott} 
    J. R. Schott.
    Fault tolerant design using single and multicriteria genetic algorithm optimization. 
    PhD thesis, Department of Aeronautics and Astronautics, Massachusetts Institute of Technology, Cambridge, MA, 1995.

    \bibitem{Schwefel} 
     H-P. Schwefel.
    Kybernetische evolution als strategie der experimentellen forschung in der stromungstechnik. 
    Technical report, Diplomarbeit Hermann Fottinger Institut fur Stromungstechnik, Technische universit at, Berlin, Germany, 1965.

    \bibitem{Fogel} 
    L. J. Fogel. Toward inductive inference automata. In
    \textit{Proceedings of the International Federation for Information Processing Congress}. 
     Munich, 1962, pp. 395–399.

    \bibitem{FogelOwens} 
    L. J. Fogel, A. J. Owens, and M. J. Walsh.
    \textit{Artificial Intelligence Through Simulated Evolution.}. 
    Wiley, 1966.

    \bibitem{Koza} 
    J. R. Koza
    \textit{Genetic Programming.}. 
    MIT Press, Cambridge, MA, 1992.

    \bibitem{BackFogelMichalewicz} 
    T. Back, D. B. Fogel, and Z. Michalewicz, editors.
    \textit{Handbook of Evolutionary Computation.}. 
    Oxford University Press, 1997.
    
    \bibitem{CorneDorigoDasguptaMoscato} 
    D. Corne, M. Dorigo, F. Glover, D. Dasgupta, P. Moscato, R. Poli, and K. V. Price.
    \textit{New ideas in optimization.}. 
    McGraw-Hill Ltd., UK, 1999.
    
    \bibitem{Moscato} 
     P. C3P Report. 826. Caltech Concurrent Computation Program; 1989. On evolution, search, optimization, genetic algorithms and martial arts: towards memetic algorithms.  
    
    \bibitem{DorigoBirattari} 
    M. Dorigo, M. Birattari, and T. Stützle. Ant colony optimization.
    \textit{Computational Intelligence Magazine}. 
    IEEE, 1(4):28–39, 2006.

    \bibitem{KarabogaBasturk} 
    D. Karaboga and B. Basturk. A powerful and efficient algorithm for numerical function optimization: artificial bee colony (abc) algorithm. 
    \textit{Journal of Global Optimization, }. 
    39(3):459–471, 2007.
    
    \bibitem{Rudolph} 
    G. Rudolph. Convergence of evolutionary algorithms in general search spaces.
    \textit{In Proceedings of the Third IEEE Conference on Evolutionary Computation,}
    1996.
    
    \bibitem{Gnanavel} 
    A. Gnanavel Babu, J. Jerald, A. Noorul Haq , V. Muthu Luxmi, T. Vigneswaralu, Scheduling of machines and automated guided vehicles in FMS using differential evolution, Int. J. Prod. Res., 48 ,2010, pp. 4683-4699.
    
    \bibitem{Melo} 
    V.V. De Melo, G.L. Carosio, Investigating multi-view differential evolution for solving constrained engineering design problems, Expert Syst. Appl., 40, 2013, pp. 3370-3377.
    
    \bibitem{Karaboga} 
    D. Karaboga. 
    An idea based on honey bee swarm for numerical optimization.. 
    Technical Report TR06, Erciyes University, 2005.
    
    \bibitem{CastroTimmis} 
    L. N. De Castro and J. Timmis.
    \textit{Artificial immune systems: a new computational intelligence approach.}. 
    Springer Science \& Business Media, 2002.
    
    \bibitem{TalbiLibro} 
    E-G Talbi
    \textit{Metaheuristics: from design to implementation}. 
    Wiley, Hoboken, 2009.
    
    \bibitem{MinettiSalto} 
    C. Bermudez, G. Minetti and C. Salto, 
    \textit{Improving Artificial Bee Colony Algorithm with Evolutionary Operators} Facultad de Ingeniería, Universidad Nacional de La Pampa, CONICET, Argentina, 2017.
    
    \bibitem{tang2011} 
    J. Tang, G. Zhang, B. Lin and B. Zhang,
    ``A hybrid algorithm for flexible job-shop scheduling problem``, 
    \textit{Procedia Engineering}, vol 15, pp. 3678 - 3683, 2011.
    
    \bibitem{Wang2012917} 
    L. Wang, S. Wang, Y. Xu, G. Zhou and M. Liu, 
    ``A bi-population based estimation of distribution algorithm for the flexible job-shop scheduling problem``, 
    \textit{Computers \& Industrial Engineering }, vol 62, no. 4, pp. 917 - 926, 2012.

    \bibitem{WANG2017} 
    L. Wang, J. Cai, M. Li and Z. Liu, 
    ``Flexible job-shop scheduling problem using an improved ant colony optimization``,
    \textit{Scientific Programming}, pp. 1 - 11, 2017.
\end{thebibliography}

