

\begin{thebibliography}{9}
    \bibitem{Goldberg} 
    D. E. Goldberg.
    \textit{Genetic Algorithms in Search, Optimization and Machine Learning}. 
    Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1st edition, 1989.

    \bibitem{Holland3} 
    Holland J. H.
    \textit{Adaptation in Natural and Artificial Systems: An Introductory Analysis with Applications to Biology, Control, and Artificial Intelligence}. 
    MIT Press; 1992.
    
    \bibitem{Moscato} 
     P. C3P Report. 826. Caltech Concurrent Computation Program; 1989. On evolution, search, optimization, genetic algorithms and martial arts: towards memetic algorithms. 

    \bibitem{StornPrice2} 
    Storn R., Price K. Differential evolution—a simple and efficient heuristic for global optimization over continuous spaces. 
    \textit{Journal of Global Optimization.}
    1997;11(4):341–359.      
     
    \bibitem{Colorni} 
    Colorni A., Dorigo M., Maniezzo V. Distributed optimization by ant colonies. Proceedings of the 1st European Conference on Artificial Life; 1991; Paris, France. pp. 134–142.
    
    \bibitem{Eberhart} 
    Eberhart R. C., Kennedy J. New optimizer using particle swarm theory. Proceedings of the 6th International Symposium on Micro Machine and Human Science; October 1995. pp. 39–43.    

    \bibitem{KarabogaBasturk} 
    D. Karaboga and B. Basturk. A powerful and efficient algorithm for numerical function optimization: artificial bee colony (abc) algorithm. 
    \textit{Journal of Global Optimization, }. 
    39(3):459–471, 2007.    

    \bibitem{Gnanavel} 
    Gnanavel Babu A., Jerald J., Noorul Haq A. , Muthu Luxmi V., Vigneswaralu T., Scheduling of machines and automated guided vehicles in FMS using differential evolution, Int. J. Prod. Res., 48 ,2010, pp. 4683-4699.
    
    \bibitem{Melo} 
    De Melo V.V., Carosio G.L., Investigating multi-view differential evolution for solving constrained engineering design problems, Expert Syst. Appl., 40, 2013, pp. 3370-3377.

    \bibitem{Ali} 
    Ali M., Zhu W.A, Penalty function-based differential evolution algorithm for constrained global optimization, Comput. Optim. Appl., 54, 2013, pp. 707-739.

    \bibitem{Juang} 
    Juang J.-G., Yu S.-T., Disturbance encountered landing system design based on sliding mode control with evolutionary computation and cerebellar model articulation controller, Appl. Math. Model., 39, 2015, pp. 5862-5881.
     
    \bibitem{Yang} 
    Yang Z., Yu Q., Dong W., Gu X., Qiao W., Liang X., Structure control classification and optimization model of hollow carbon nanosphere core polymer particle based on improved differential evolution support vector machine, Appl. Math. Model., 37, 2013, pp. 7442-7451    
    
    \bibitem{GareyJohnson} 
    Garey M. R., Johnson D. S., Sethi R., The complexity of flowshop and jobshop scheduling, Math. Oper. Res., vol. 1, no. 2, 1976, pp. 117–129.
    

\end{thebibliography}

